---
title: "Assignment 5"
author: "Kimaya Rane, Ryan Nguyen, Rod Vasquez"
date: "10/3/2017"
output: html_document
---

```{r}
library(readxl)
tallestbuildings=read_excel("tallestbuildings.xlsx")
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
```
## Number of buildings there are there in each city represented in the dataset 

```{r}
colnames(tallestbuildings)
head(tallestbuildings)
names(tallestbuildings)[2]="Building"
names(tallestbuildings)
```

```{r}
colnames(tallestbuildings)
```

```{r}
tallestbuildings %>% group_by(City) %>% summarise(cnt = n()) %>% arrange(desc(cnt))
```

## Different cities plotted in order of the mean height (in feet) of buildings in a city

```{r}
colnames(tallestbuildings)
head(tallestbuildings)
names(tallestbuildings)[6]="Height"
names(tallestbuildings)[5]="Height.Ft"
names(tallestbuildings)

```

```{r}
tallestbuildings %>% group_by(City) %>%
  summarise(Mean.Height=mean(Height)) %>%
  ggplot(aes(x= reorder(City,-Mean.Height),y=Mean.Height)) +
  geom_bar(stat = "identity") + coord_flip() + labs(list(title = "Cities Ranked by Mean Height", x = "Cities", y = "Mean Height"))
```

## Number of buildings there are in each country represented in the dataset 

```{r}
library(countrycode)
```

```{r}
tallestbuildings=tallestbuildings %>% separate(City,c("City","Country"),sep="[:punct:]")
```

```{r}
tallestbuildings$Country = countrycode(tallestbuildings$Country,"iso2c","country.name")
```

```{r}
tallestbuildings%>%group_by(Country) %>% summarise(numBuildings = n()) %>%
    arrange(desc(numBuildings)) %>%
    ggplot(aes(y=numBuildings, x=reorder(Country, numBuildings))) +
    geom_bar(stat = "identity", fill = "red") + coord_flip() + labs(list(title = "Number of Buildings per Country", x = "Country", y = "Number of Buildings"))
```

## Mean height (in feet) of buildings in each country

```{r}
tallestbuildings %>% group_by(Country) %>%
  summarise(Mean.Height=mean(Height)) %>%
  ggplot(aes(x= reorder(Country,Mean.Height),y=Mean.Height)) +
  geom_bar(stat = "identity", fill = "purple") + coord_flip() + labs(list(title = "Mean Height(ft) of Buildings by Country", x = "Country", y = "Mean Height"))
```

## Adding color to the plot above 

```{r}
tallestbuildings %>% group_by(Country) %>%
  summarise(Mean.Height=mean(Height)) %>%
  ggplot(aes(x= reorder(Country,Mean.Height),y=Mean.Height)) +
  geom_bar(stat = "identity") + coord_flip() + labs(list(title = "Mean Height(ft) of Buildings by Country", x = "Country", y = "Mean Height"))

 bldgct = tallestbuildings %>% group_by(Country) %>% summarise(Building_Count = n(),  Mean.Height=mean(Height))
    head(bldgct)
    
    bldgct %>%
  ggplot(aes(x= reorder(Country,Mean.Height),y=Mean.Height, fill = as.factor(Building_Count))) +
  geom_bar(stat = "identity",position="dodge") + coord_flip() + scale_fill_brewer(palette="Paired") + labs(list(title = "Mean Height(ft) of Buildings by Country", x = "Country", y = "Mean Height"))
```


## Mean heights (in feet) of buildings that are used for different purposes

```{r}
 bldgn = tallestbuildings %>% group_by(Use) %>%
  summarise(Mean.Height=mean(Height))
  head(bldgn)
  
  bldgn %>%
  ggplot(aes(x= reorder(Use,Mean.Height),y=Mean.Height)) +
  geom_bar(stat = "identity",position="dodge", fill = "blue") + coord_flip() + labs(list(title = "Mean Height(ft) of Different Purposes", x = "Uses", y = "Mean Height"))
```

## Summary
In conclusion, Dubai has the largets number of buildings at 18. However, Mecca has the largest average of tall buildings out of all the cities. Next Taiwan has is the country with the largest average for building height. Lastly, office/residential/hotel are the type of buildings that have the largest average height.









